TODO \thanks{ The original version of this paper is entitled ``Interactive Checks for Coordination Avoidance'' and was published in PVLDB Vol.\ 12. }

### 2020-05-16 doc/sigmod_paper/invariant_confluence.tex
Cut merge reduction section; split acks out.

{\input{sections/abstract}}
{\input{sections/introduction}}
{\input{sections/invariant_confluence}}
{\input{sections/invariant_closure}}
{\input{sections/interactive_decision_procedure}}
{\input{sections/merge_reduction}}
{\input{sections/segmented_invariant_confluence.tex}}
{\input{sections/evaluation}}
{\input{sections/related_work}}
{\input{sections/conclusion}}

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
This section is optional; it is a location for you
to acknowledge grants, funding, editing assistance, collaboration, access to
uncommon, but necessary, hardware or software etc.
In the present case, for example, the
authors would like to thank Gerald Murray of ACM for
his help in codifying this \textit{Author's Guide}
and the \textbf{.cls} and \textbf{.tex} files that it describes.

>>>>

{\input{sections/abstract}}
{\input{sections/introduction}}
{\input{sections/invariant_confluence}}
{\input{sections/invariant_closure}}
{\input{sections/interactive_decision_procedure}}
{\input{sections/segmented_invariant_confluence.tex}}
{\input{sections/evaluation}}
{\input{sections/related_work}}
{\input{sections/conclusion}}
{\input{sections/acknowledgements}}
